% RetrievalBench -- evidence-aligned anonymous AKBC submission.
% Standalone Overleaf file: paste as main.tex. If akbc2027.sty or akbc.sty is
% present, it uses that style; otherwise it falls back to AKBC's historical
% single-column, ICLR-like layout.
\documentclass[10pt,letterpaper]{article}
\makeatletter
\newif\ifakbcsty\akbcstyfalse
\IfFileExists{akbc2027.sty}{\usepackage{akbc2027}\akbcstytrue}{%
  \IfFileExists{akbc.sty}{\usepackage{akbc}\akbcstytrue}{}}
\makeatother
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{multirow}
\usepackage{array}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{enumitem}
\ifakbcsty\else
  \usepackage[letterpaper,textwidth=5.5in,textheight=9in,headheight=14pt,headsep=22pt]{geometry}
  \usepackage{times}
  \usepackage{fancyhdr}
  \pagestyle{fancy}\fancyhf{}
  \fancyhead[C]{\small\itshape Under review as a conference paper at AKBC}
  \fancyfoot[C]{\small\thepage}
  \renewcommand{\headrulewidth}{0.4pt}
  \usepackage{titlesec}
  \titleformat{\section}{\large\bfseries\scshape}{\thesection}{0.8em}{}
  \titleformat{\subsection}{\normalsize\bfseries\scshape}{\thesubsection}{0.8em}{}
  \titlespacing*{\section}{0pt}{14pt plus 2pt minus 2pt}{6pt}
  \titlespacing*{\subsection}{0pt}{10pt plus 2pt minus 2pt}{4pt}
\fi
\captionsetup{font=small,labelfont=bf,skip=6pt}
\usepackage[hidelinks]{hyperref}
\setlist{nosep,leftmargin=*}

\title{RetrievalBench: Chunking and Embedding Choice as\\
First-Class Variables in Cross-Domain Retrieval Evaluation}
\author{Anonymous AKBC Submission}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Standard retrieval benchmarks evaluate systems over pre-segmented corpora, leaving document
segmentation outside the experimental design. Production retrieval systems do not have this
luxury: documents must be divided into retrievable units, and the segmentation policy may
interact with both the corpus and the embedding model. We present \textbf{RetrievalBench}, a
cross-domain evaluation framework that treats chunking strategy and embedding-model choice as
controlled experimental variables. Our main study is a complete sensitivity matrix over twelve
domains, four chunking strategies, and three dense embedding models, with BM25 included as a
sparse reference and bootstrap confidence intervals computed for every configuration. Chunking
is not a neutral preprocessing step: holding the retriever and corpus fixed, its selection changes
NDCG@10 by as much as 47\% relative, and no chunker is uniformly best. We introduce the
Chunking Sensitivity Index (CSI) and Embedding Sensitivity Index (ESI), a per-domain variance
decomposition that identifies which decision deserves greater tuning attention. CSI exceeds ESI
in 5 of 12 domains, especially in several structured or long-form collections, whereas embedding
choice dominates in many short-passage matching tasks. These results replace the claim that
``chunking always matters more'' with a domain-dependent diagnostic. The framework additionally
records retrieval-stage latency and metered embedding-API usage, but we treat these measurements
as exploratory rather than universal deployment estimates.
\end{abstract}

\section{Introduction}

Retrieval evaluation is commonly built around a fixed corpus of atomic documents, a query set,
relevance judgments, and a ranking metric such as NDCG@10 \cite{thakur2021beir}. This abstraction
has enabled reproducible comparison across domains, but it hides a consequential decision faced
by deployed retrieval systems: source documents must often be segmented before they can be
indexed. A financial report can be split into windows, sentences, paragraphs, or semantically
coherent groups. Each choice changes the units presented to the retriever and, consequently, the
ranking that is evaluated.

Chunking is frequently discussed as an implementation detail. That treatment is questionable for
two reasons. First, chunk boundaries determine which evidence is represented by a single vector or
sparse document. Second, a chunking rule can interact with the embedding model: two models may
respond differently to short sentences, long windows, and mixed-topic passages. Evaluating one
fixed segmentation therefore risks attributing a preprocessing effect to the retriever itself.

RetrievalBench makes these decisions explicit. For each domain, we construct four chunked
variants of a common document sample and evaluate dense retrieval with three embedding models.
We include BM25 as a sparse reference, propagate document-level relevance judgments to chunks by
parent-document identity, and aggregate retrieved chunks back to documents for evaluation. The
result is not intended as a new absolute leaderboard. Because the main matrix uses controlled
subsamples, it supports within-matrix comparisons among chunkers and embedders rather than
comparison with full-corpus leaderboard scores.

Our contributions are:
\begin{enumerate}
    \item A controlled cross-domain benchmark covering twelve domains, four operationally
    specified chunking strategies, three dense embedding models, and a BM25 reference.
    \item Empirical evidence that chunking choice changes NDCG@10 by up to 47\% relative and
    interacts with both domain and retrieval model; no single strategy is uniformly best.
    \item CSI and ESI, variance-based diagnostics that compare chunking sensitivity with
    embedding-model sensitivity within each domain. The analysis shows that their relative
    importance is domain-dependent rather than universal.
    \item An artifact-oriented evaluation implementation with bootstrap uncertainty estimates,
    paired-comparison utilities, metered OpenAI embedding usage, and optional latency and
    reranking analyses. We distinguish these supported capabilities from the central matrix claims.
\end{enumerate}

\section{Related Work}

\textbf{Cross-domain retrieval evaluation.}
BEIR standardized heterogeneous zero-shot retrieval evaluation across biomedical, scientific,
financial, fact-checking, question-answering, and other domains \cite{thakur2021beir}. Reproducible
IR toolkits have similarly made sparse and dense baselines easier to compare \cite{lin2021pyserini}.
RetrievalBench retains standard document-level metrics but varies the segmentation under which a
document is indexed.

\textbf{Dense retrieval and embedding models.}
Dense passage retrieval represents queries and candidate text in a shared vector space
\cite{karpukhin2020dpr}. General-purpose embedding benchmarks broadened evaluation across tasks
\cite{muennighoff2023mteb}, while model families such as E5 and BGE provide strong compact
retrievers \cite{wang2022e5,xiao2023cpack}. Our focus is not a new embedding architecture, but the
interaction between the embedder and the chunked units it consumes.

\textbf{Chunking and reranking.}
Fixed windows, sentence grouping, recursive splitting, and semantic grouping are widely available
in RAG tooling, yet they are rarely crossed systematically with both domain and embedding choice.
Cross-encoder reranking is a standard second stage \cite{nogueira2019passage}. RetrievalBench
supports reranking, but the central sensitivity matrix deliberately excludes reranked arms so that
CSI and ESI measure chunking and embedding effects without introducing a second-stage model.

\section{Experimental Framework}

\subsection{Domains and sampling}

The matrix contains twelve public-data domains: finance (FiQA), legal question answering
(Open Australian Legal QA), biomedical retrieval (TREC-COVID), medical retrieval (NFCorpus),
scientific claim verification (SciFact), technical literature retrieval (SciDocs), argumentation
(ArguAna), community duplicate-question retrieval (Quora), open-domain question answering
(Natural Questions), entity retrieval (DBpedia-Entity), fact checking (FEVER), and multi-hop
question answering (HotpotQA).

For comparability and tractable repeated indexing, we apply a seeded sampling policy. Each corpus
contains 2,000 sampled fill documents plus every document referenced by the retained relevance
judgments. Consequently, a corpus can exceed 2,000 documents when the relevant set alone is
larger. We retain at most 500 seeded-sampled queries, except where the dataset contains fewer
eligible queries or where the legal collection is evaluated in full. Sampling uses seed 42.
Table~\ref{tab:data} reports the realized sizes.

\begin{table}[t]
\centering
\caption{Domains and realized matrix sizes. Corpus subsampling always retains qrels-relevant
documents, so some collections exceed 2,000 documents.}
\label{tab:data}
\small
\begin{tabular}{llrr}
\toprule
Domain & Dataset & Documents & Queries \\
\midrule
Finance & fiqa & 2,000 & 500 \\
Legal & auslegalqa & 2,099 & 2,124 \\
Biomedical & trec-covid & 17,537 & 50 \\
Argumentation & arguana & 1,999 & 500 \\
Open-domain QA & nq & 2,000 & 500 \\
Medical & nfcorpus & 3,128 & 323 \\
Scientific & scifact & 2,000 & 300 \\
Technical & scidocs & 2,180 & 500 \\
Community & quora & 2,000 & 500 \\
Fact checking & fever & 2,000 & 500 \\
Multi-hop QA & hotpotqa & 2,000 & 500 \\
Entity retrieval & dbpedia-entity & 14,877 & 400 \\
\bottomrule
\end{tabular}
\end{table}

Subsampling reduces the number of distractors and can inflate absolute effectiveness. We therefore
use the matrix to compare configurations evaluated on the same sampled corpus; we do not present
its absolute scores as BEIR leaderboard replacements.

\subsection{Operational chunking strategies}

We evaluate four strategies, described here according to the implementation used to produce the
reported matrix:
\begin{itemize}
    \item \textbf{Fixed-512}: non-overlapping progress through whitespace-delimited text using
    windows of at most 512 words and an overlap of 50 words.
    \item \textbf{Sentence}: non-overlapping windows of three sentences, using NLTK sentence
    segmentation.
    \item \textbf{Recursive}: split first on blank-line paragraph boundaries; paragraphs exceeding
    512 whitespace-delimited words are split into sentences.
    \item \textbf{Semantic}: embed sentences with OpenAI
    \texttt{text-embedding-3-small} and greedily merge adjacent sentences when cosine similarity
    is at least 0.75. These boundaries are computed independently of the downstream dense
    retriever and reused across embedding-model comparisons.
\end{itemize}

These names are operational labels rather than claims that the implementations exhaust all
possible fixed, sentence-based, recursive, or semantic chunkers. This distinction is important:
our conclusions concern sensitivity to these four concrete policies.

\subsection{Retrievers and embedders}

The sparse reference is BM25. Dense retrieval uses OpenAI
\texttt{text-embedding-3-small} (1,536 dimensions),
\texttt{BAAI/bge-small-en-v1.5} (384 dimensions), and
\texttt{intfloat/e5-small-v2} (384 dimensions). BGE queries use the model's retrieval instruction;
E5 queries and passages use the \texttt{query:} and \texttt{passage:} prefixes. Embeddings are
L2-normalized and scored by inner product.

For each query, the retriever selects the top 50 chunks. Chunk scores are aggregated to their parent
documents by maximum score, and the top 10 unique documents are evaluated. Relevance is inherited
from document-level qrels: a retrieved chunk is treated as evidence for its parent document, but no
claim is made that every chunk of a relevant document is independently relevant.

\subsection{Metrics and uncertainty}

We report NDCG@10 as the primary metric, with Recall@10, MRR, and MAP available in the result
artifacts. For each configuration, we compute a 95\% bootstrap confidence interval over per-query
NDCG using 1,000 seeded resamples. The framework also implements paired permutation tests and
Cohen's $d$ for analyses where aligned per-query values are retained.

\subsection{Chunking and embedding sensitivity}
\label{sec:indices}

For a fixed domain, let $M_{c,e}$ denote NDCG@10 for dense retrieval with chunker $c$ and
embedder $e$. Let $C$ and $E$ be the sets of four chunkers and three embedders. We define
\begin{align}
\mathrm{CSI} &=
\frac{\frac{1}{|E|}\sum_{e\in E}\mathrm{Var}_{c\in C}(M_{c,e})}
     {\mathrm{Var}_{c\in C,e\in E}(M_{c,e})}, \\
\mathrm{ESI} &=
\frac{\frac{1}{|C|}\sum_{c\in C}\mathrm{Var}_{e\in E}(M_{c,e})}
     {\mathrm{Var}_{c\in C,e\in E}(M_{c,e})}.
\end{align}
CSI $>$ ESI means that, within the evaluated pool, changing chunkers moves effectiveness more
than changing embedders on average. The indices are diagnostics, not percentages of variance in a
fully orthogonal ANOVA: interaction can cause CSI and ESI not to sum to one.

\section{Results}

\subsection{Chunking changes retrieval effectiveness}

Table~\ref{tab:matrix} reports the complete matrix. Chunking causes substantial within-system
variation. The largest observed relative swing is for biomedical BM25, from 0.476 with semantic
chunking to 0.700 with fixed-512:
$(0.700-0.476)/0.476=47.1\%$. Finance shows a similarly consistent pattern across all three dense
models: fixed-512 exceeds semantic by 26\% relative for OpenAI, 40\% for BGE, and 41\% for E5.

The best chunker is neither global nor model-independent. Recursive and fixed windows are often
competitive on long or structured text, while sentence or semantic policies sometimes win in other
domains. Quora supplies a useful boundary condition: its documents are already short and nearly
atomic, so all four policies produce almost identical scores. This supports a qualified conclusion:
chunking sensitivity depends strongly on the units present in the source corpus.

\begin{table*}[t]
\centering
\caption{NDCG@10 for the complete sensitivity matrix. BM25 is a sparse reference; the three dense
columns form the $4\times3$ matrix used for CSI/ESI. Compare configurations within a domain, not
with full-corpus leaderboards.}
\label{tab:matrix}
\scriptsize
\setlength{\tabcolsep}{4.5pt}
\begin{tabular}{llrrrr}
\toprule
Domain & Chunker & BM25 & Dense--OpenAI & Dense--BGE & Dense--E5 \\
\midrule
\multirow{4}{*}{Finance} & Sentence & .285 & .676 & .627 & .607 \\
 & Fixed-512 & .346 & .739 & .677 & .665 \\
 & Recursive & .329 & .726 & .663 & .624 \\
 & Semantic & .254 & .585 & .485 & .471 \\
\midrule
\multirow{4}{*}{Legal} & Sentence & .688 & .793 & .764 & .811 \\
 & Fixed-512 & .732 & .816 & .771 & .824 \\
 & Recursive & .732 & .816 & .771 & .824 \\
 & Semantic & .659 & .765 & .666 & .764 \\
\midrule
\multirow{4}{*}{Biomedical} & Sentence & .619 & .928 & .916 & .907 \\
 & Fixed-512 & .700 & .948 & .964 & .920 \\
 & Recursive & .690 & .943 & .944 & .906 \\
 & Semantic & .476 & .879 & .854 & .839 \\
\midrule
\multirow{4}{*}{Argumentation} & Sentence & .416 & .571 & .557 & .492 \\
 & Fixed-512 & .419 & .566 & .598 & .536 \\
 & Recursive & .434 & .569 & .599 & .537 \\
 & Semantic & .363 & .503 & .471 & .428 \\
\midrule
\multirow{4}{*}{Open-domain QA} & Sentence & .816 & .980 & .978 & .975 \\
 & Fixed-512 & .839 & .980 & .979 & .981 \\
 & Recursive & .841 & .979 & .979 & .965 \\
 & Semantic & .785 & .985 & .960 & .950 \\
\midrule
\multirow{4}{*}{Medical} & Sentence & .269 & .399 & .363 & .329 \\
 & Fixed-512 & .280 & .403 & .357 & .340 \\
 & Recursive & .279 & .402 & .357 & .334 \\
 & Semantic & .251 & .386 & .368 & .316 \\
\midrule
\multirow{4}{*}{Scientific} & Sentence & .583 & .797 & .785 & .717 \\
 & Fixed-512 & .635 & .798 & .784 & .764 \\
 & Recursive & .638 & .792 & .780 & .746 \\
 & Semantic & .522 & .778 & .755 & .706 \\
\midrule
\multirow{4}{*}{Technical} & Sentence & .309 & .428 & .407 & .338 \\
 & Fixed-512 & .327 & .439 & .434 & .392 \\
 & Recursive & .328 & .434 & .432 & .344 \\
 & Semantic & .281 & .412 & .394 & .326 \\
\midrule
\multirow{4}{*}{Community} & Sentence & .955 & .997 & .998 & .996 \\
 & Fixed-512 & .955 & .997 & .998 & .996 \\
 & Recursive & .955 & .997 & .998 & .996 \\
 & Semantic & .954 & .997 & .997 & .991 \\
\midrule
\multirow{4}{*}{Fact checking} & Sentence & .954 & .986 & .984 & .989 \\
 & Fixed-512 & .949 & .985 & .984 & .988 \\
 & Recursive & .936 & .984 & .983 & .987 \\
 & Semantic & .939 & .985 & .987 & .987 \\
\midrule
\multirow{4}{*}{Multi-hop QA} & Sentence & .850 & .937 & .932 & .949 \\
 & Fixed-512 & .856 & .942 & .931 & .949 \\
 & Recursive & .856 & .942 & .931 & .949 \\
 & Semantic & .823 & .938 & .929 & .937 \\
\midrule
\multirow{4}{*}{Entity retrieval} & Sentence & .644 & .855 & .821 & .842 \\
 & Fixed-512 & .651 & .860 & .823 & .865 \\
 & Recursive & .651 & .860 & .824 & .865 \\
 & Semantic & .618 & .846 & .825 & .792 \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Chunking versus embedding is domain-dependent}

Table~\ref{tab:csi} summarizes the variance decomposition. CSI exceeds ESI in 5 of 12 domains:
TREC-COVID, FiQA, ArguAna, Natural Questions, and the legal collection. Embedding choice dominates
strongly in NFCorpus, SciDocs, HotpotQA, SciFact, Quora, and FEVER. DBpedia-Entity is relatively
balanced but remains embedding-dominant under the strict comparison.

\begin{table}[t]
\centering
\caption{Chunking and embedding sensitivity for pure dense retrieval.}
\label{tab:csi}
\small
\begin{tabular}{llrrc}
\toprule
Domain & Dataset & CSI & ESI & CSI$>$ESI \\
\midrule
Biomedical & trec-covid & .858 & .184 & Yes \\
Finance & fiqa & .770 & .244 & Yes \\
Argumentation & arguana & .723 & .338 & Yes \\
Open-domain QA & nq & .710 & .677 & Yes \\
Entity retrieval & dbpedia-entity & .643 & .717 & No \\
Legal & auslegalqa & .566 & .507 & Yes \\
Fact checking & fever & .483 & .787 & No \\
Community & quora & .381 & .856 & No \\
Scientific & scifact & .292 & .800 & No \\
Multi-hop QA & hotpotqa & .223 & .874 & No \\
Technical & scidocs & .222 & .826 & No \\
Medical & nfcorpus & .059 & .985 & No \\
\bottomrule
\end{tabular}
\end{table}

These results reject both simple extremes. Chunking is not merely preprocessing, because it can
move quality substantially while the retriever is fixed. But it is also not universally more important
than the embedding model. A practical reading is to estimate both sensitivities on a representative
sample: prioritize chunking experiments when CSI is high, model selection when ESI is high, and
joint tuning when the values are close.

The result is conditional on the evaluated model pool. The two local embedders are similarly sized
small models, whereas the API model belongs to a different capacity and training regime. This may
increase observed embedding variance. Conversely, the four chunkers represent only one
parameterization of each strategy family. CSI and ESI should therefore be interpreted as properties
of a domain under a declared candidate set, not immutable corpus constants.

\subsection{Exploratory deployment measurements}

RetrievalBench records metered OpenAI token usage and supports a latency-discounted score,
\begin{equation}
\mathrm{LA\mbox{-}NDCG}@10 = \mathrm{NDCG}@10
\exp\!\left(-\frac{\max(0,\ell-B)}{B}\right),
\end{equation}
where $B$ is a user-selected latency budget. We include these facilities because deployment choices
depend on more than effectiveness. However, the archived latency runs were collected on a single
machine and do not share a fully production-complete online boundary: offline indexing is excluded,
and dense timing does not include all API/network overhead. We therefore do not use them to claim a
universal system reordering. They are examples of how the framework can be applied once a deployment
defines its own measurement boundary.

The reported cost field is similarly narrow: it is metered OpenAI embedding API spend at the price
used during the experiments. It includes OpenAI calls used for semantic segmentation and OpenAI
dense embeddings, but assigns no monetary value to local-model compute, hardware, energy, or
reranker inference. It should not be interpreted as total serving cost.

\section{Discussion}

\textbf{Chunking is part of the evaluated system.}
If two studies evaluate the same embedder using different segmentation policies, their scores need
not estimate the same system. Benchmark reports should therefore publish chunker code and
parameters alongside model identifiers and retrieval depth.

\textbf{Short-document domains are an informative control.}
The near-zero spread on Quora shows that a benchmark need not reward arbitrary chunker complexity.
When documents are already atomic, segmentation has little room to change the indexed unit. This
also cautions against extrapolating chunking conclusions from passage collections to long documents.

\textbf{Sensitivity indices guide experimental allocation.}
CSI and ESI do not nominate a universal winner. Their value is operational: a small pilot matrix can
show whether engineering time is better spent exploring segmentation, models, or their interaction.

\section{Limitations}

First, the main matrix uses one seeded corpus/query sample per domain. Although every configuration
within a domain shares that sample, additional seeds would better quantify sensitivity to distractor
selection. Second, propagating document-level qrels to parent-linked chunks does not identify which
specific chunk contains the judged evidence; chunk-level annotation would support a stricter analysis.
Third, absolute matrix scores are inflated by subsampling and must not be compared directly with
full-corpus leaderboards.

Fourth, the embedder pool mixes an API model with two similarly sized open-source models; a
same-capacity model pool would be a useful robustness check. Fifth, the four chunkers are concrete,
relatively simple implementations. Different tokenizers, sentence windows, recursive separators,
semantic thresholds, and overlap values could change CSI. Sixth, semantic boundaries are generated
with the OpenAI model for all downstream embedders; this controls the segmentation across systems
but may favor semantic judgments aligned with that model.

Finally, latency, reranking, and monetary cost are supported by the framework but are not established
here as universal cross-domain conclusions. Existing latency runs use a single environment and a
limited timing boundary, local compute is not monetized, and some archived reranker runs produced
unchanged rankings on out-of-domain tasks. We retain these analyses as exploratory artifacts rather
than treating them as central evidence.

\section{Conclusion}

RetrievalBench evaluates a decision that fixed-corpus benchmarks usually hide. Across twelve
domains, changing only the chunking strategy changes NDCG@10 by as much as 47\% relative, and
the preferred strategy varies across domains and retrievers. CSI and ESI further show that the
chunking-versus-embedding question has no universal answer: chunking dominates in 5 of 12 domains,
while embedding choice dominates in the remainder of the evaluated pool. The broader lesson is
methodological. Segmentation should be reported and evaluated as part of the retrieval system, and
its importance should be measured rather than assumed.

\section*{Artifact and Reproducibility Statement}

The repository contains the per-domain aggregate result files used for Tables~\ref{tab:matrix} and
\ref{tab:csi}, the seeded sampling and experiment runner, bootstrap metric implementation, and
CSI/ESI analysis script. The reported matrix was generated with:
\begin{verbatim}
RB_MAX_CORPUS=2000 RB_MAX_QUERIES=500 \
python scripts/run_chunking_pipeline.py --dataset <dataset> \
  --embedders openai bge-small e5-small
\end{verbatim}
Some large-relevant-set collections exceed the nominal corpus cap because all qrels-relevant
documents are retained. Aggregate artifacts are available for all twelve domains. Complete
per-query ranked-list sidecars are not available for every historical run; accordingly, we do not
claim that every published aggregate can be reconstructed from ranked lists alone. A table-generation
and artifact-validation script should accompany the archival release to verify domain, chunker,
embedder, and value completeness directly from the released JSON files.

\begin{thebibliography}{99}

\bibitem{thakur2021beir}
N. Thakur, N. Reimers, A. R\"uckl\'e, A. Srivastava, and I. Gurevych.
BEIR: A heterogeneous benchmark for zero-shot evaluation of information retrieval models.
\emph{NeurIPS Datasets and Benchmarks}, 2021.

\bibitem{lin2021pyserini}
J. Lin, X. Ma, S.-C. Lin, J.-H. Yang, R. Pradeep, and R. Nogueira.
Pyserini: A Python toolkit for reproducible information retrieval research with sparse and dense
representations. \emph{SIGIR}, 2021.

\bibitem{karpukhin2020dpr}
V. Karpukhin, B. O\u{g}uz, S. Min, P. Lewis, L. Wu, S. Edunov, D. Chen, and W.-t. Yih.
Dense passage retrieval for open-domain question answering. \emph{EMNLP}, 2020.

\bibitem{muennighoff2023mteb}
N. Muennighoff, N. Tazi, L. Magne, and N. Reimers.
MTEB: Massive text embedding benchmark. \emph{EACL}, 2023.

\bibitem{wang2022e5}
L. Wang, N. Yang, X. Huang, B. Jiao, L. Yang, D. Jiang, R. Majumder, and F. Wei.
Text embeddings by weakly-supervised contrastive pre-training.
\emph{arXiv:2212.03533}, 2022.

\bibitem{xiao2023cpack}
S. Xiao, Z. Liu, P. Zhang, and N. Muennighoff.
C-Pack: Packaged resources to advance general Chinese embedding.
\emph{SIGIR}, 2024.

\bibitem{nogueira2019passage}
R. Nogueira and K. Cho.
Passage re-ranking with BERT. \emph{arXiv:1901.04085}, 2019.

\end{thebibliography}

\end{document}
